## Step 1: Load packages

install.packages("tidyverse")
install.packages("skimr")
install.packages("janitor")


library(tidyverse)
library(skimr)
library(janitor)

## Step 2: Import data
The data in this example is originally from the article Hotel Booking Demand Datasets (https://www.sciencedirect.com/science/article/pii/S2352340918315191), written by Nuno Antonio, Ana Almeida, and Luis Nunes for Data in Brief, Volume 22, February 2019.


You can learn more about the dataset here:
https://www.kaggle.com/jessemostipak/hotel-booking-demand

bookings_df <- read_csv("hotel_bookings.csv")
```
## Step 3: Getting to know your data

```{r}
head(bookings_df)
```

I summarized or previewed the data with the `str()` and `glimpse()` functions to get a better understanding of the data by running the code chunks below:

```{r}
str(bookings_df)
```

```{r}
glimpse(bookings_df)
```

I used `colnames()` to check the names of the columns in my data set:

```{r}
colnames(bookings_df)
```

I used the `skim_without_charts()` function from the `skimr` package by running the code below:

```{r}
skim_without_charts(bookings_df)
```
## Step 4: Cleaning your data

Based on my notes I am primarily interested in the following variables: hotel, is_canceled, lead_time. I Created a new data frame with just those columns, calling it `trimmed_df`.

```{r}
trimmed_df <- bookings_df %>% 
  select(hotel, is_canceled, lead_time)
```

Renamed the variable 'hotel' to be named 'hotel_type' to be crystal clear on what the data is about:

```{r}
trimmed_df %>% 
  select(hotel, is_canceled, lead_time) %>% 
  rename(hotel_type = hotel)
```

I combined the arrival month and year into one column using the unite() function:

```{r}
example_df <- bookings_df %>%
  select(arrival_date_year, arrival_date_month) %>% 
  unite(arrival_month_year, c("arrival_date_month", "arrival_date_year"), sep = " ")
```

## Step 5: Another way of doing things

I used the`mutate()` function to make changes to my columns.

```{r}
example_df <- bookings_df %>%
  mutate(guests = adults + children + babies)

head(example_df)
```

```{r}
example_df <- bookings_df %>%
  summarize(number_canceled = sum(is_canceled),
            average_lead_time = mean(lead_time))

head(example_df)
```
